Optogenetic Maxwell Demon to Exploit Intrinsic Noise and Control Cell Differentiation Despite Time Delays and Extrinsic Variability

### 2023-04-06 paper.tex
update

\begin{figure*}
\begin{center}
\includegraphics[width=1\textwidth]{GranularityScore.eps}
\caption{}
\label{}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1\textwidth]{CalculationSpeed.eps}
\caption{}
\label{Speed}
\end{center}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=1\textwidth]{GranularityScore.eps}
\caption{Effect of scale changes on control score. (A)Time series trajectory of score versus time shows that when the switch occurs at t=0, scores generally increase to a high value above 700, then drop over time. The time scale for $\alpha=1.0$ to reach steady state again is approx. 1000, 2000, and 4000 minutes for $\alpha=[1.0, 2.0, 4.0]$ respectively. Additionally, the noise floor of each system drops as a function of alpha. (B and C) time series plots of simulated SSA trajectories show that time scale to reach equilibrium changes with $\alpha$, and that an intermediate transition state becomes more visible $\alpha=4.0$. The low noise floor seen in (A) can be confimed in the trajectories as well. }
\label{}
\end{center}
\end{figure*}
